Hydra Battles and Cie

### 2021-09-13 doc/chapter-powers.tex
Alectryon: chapter on addition chains half done

\begin{Coqsrc}
Lemma exponent_pos2nat : forall c: chain,  parametric c -> 
  the_exponent_nat c = Pos.to_nat (the_exponent c).

Lemma exponent_pos_of_nat : forall c: chain,  parametric c -> 
  the_exponent c = Pos.of_nat (the_exponent_nat c).

Lemma param_correctness (c:chain) :
   parametric c -> 
   chain_correct (the_exponent c) c. 
Proof.
  intros; rewrite  exponent_pos_of_nat; auto.
  red;  rewrite  exponent_pos2nat;auto.
  rewrite Pos2Nat.id,  <- exponent_pos2nat;auto.
  apply param_correctness_nat; auto.
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Ltac parametric_tac  := 
match goal with [ |- parametric ?c] =>
   red ; intros;
   repeat (right;[assumption | assumption | ]);  
   left; assumption
end.

Example P87 : parametric C87.
Proof. Time parametric_tac. 
\end{Coqsrc}

\begin{Coqanswer}
Finished transaction in 0.005 secs (0.005u,0.s) (successful)
\end{Coqanswer}

\begin{Coqsrc}
Qed. 
\end{Coqsrc}

@@

\begin{Coqsrc}
Ltac param_chain_correct :=
match goal with 
[|- chain_correct ?p ?c ] => 
apply param_correctness; parametric_tac
end.

Lemma C87_ok' : chain_correct 87 C87.
Time param_chain_correct.
\end{Coqsrc}

\begin{Coqanswer}
Finished transaction in 0.005 secs (0.005u,0.s) (successful)
\end{Coqanswer}

\begin{Coqsrc}
Qed.
\end{Coqsrc}

@@

\begin{Coqbad}
Definition any_chain_parametric : Type :=
 forall c:chain, parametric c.

Goal any_chain_parametric.
Proof.
intros c A B R a b ; induction c.
\end{Coqbad}

\begin{Coqanswer}
 2 subgoals, subgoal 1 (ID 556)

  c : chain
  A : Type
  B : Type
  R : A -> B -> Type
  a : A
  b : B
  a0 : A
  ============================
   R a b -> computation_R R (Return a0) (c B b)

...
\end{Coqanswer}

>>>>

\inputsnippets{Addition_Chains/exponentPosToNat}
\inputsnippets{Addition_Chains/exponentPosOfNat}
\inputsnippets{Addition_Chains/paramCorrectness}

@@

\inputsnippets{Addition_Chains/parametricTac}

@@

\inputsnippets{Addition_Chains/paramChainCorrect}

@@

\inputsnippets{Addition_Chains/VeryBad,Addition_Chains/VeryBad2}
